### 2017-01-16 papers.tex
Adds another comment

Paper is \cite{ind_007}. Lists a lot of resources for other DM in \gls{lms}.

@@

What is taken from this paper is the argument that ``(\dots) one of the most
useful DM tasks in e-learning is classification''.

\begin{itemize}
    \item Discover potential student groups with similar characteristics and
        reactions to a particular pedagogical strategy; \TODO{Yet to be
        explore}
    \item Detect students' misuse or game-playing; \TODO{Yet to be explore}
    \item Group students who are hint-driven or failure-driven and find common
        misconceptions that students possess; \TODO{Yet to be explore}
    \item Identify learners with low motivation and find remedial actions to
        lower drop-out rates; \TODO{Yet to be explore}
    \item Predict/classify students when using intelligent tutoring systems;
        \TODO{Yet to be explore}
\end{itemize}

@@

\begin{itemize}
    \item Predicting students' grades from test scores using neural networks;
        \TODO{Yet to be explore}
    \item Predicting student academic success (classes that are successful or
        not) using discriminant function analysis; \TODO{Yet to be explore}
    \item Classifying students using genetic algorithms to predict their final
        grade; \TODO{Yet to be explore}
    \item Predicting a student's academic success (to classify as low, medium
        and high risk classes) using different data mining methods; \TODO{Yet
        to be explore}
    \item Predicting a student’s marks (pass and fail classes) using regression
        techniques in Hellenic Open University data; \TODO{Yet to be explore}
    \item Using neural network models from Moodle logs; \TODO{Yet to be
        explore}
\end{itemize}

@@

\WORKON{Need to finish this paper's comment}

@@

\gls{lms} systems, like Moodle, generate logs which describe that activities of
it's users. Those logs contain entries for when students login, when they ask
questions, when they offer proposals on so on. Analysing these logs in order to
understand if student performance is good or bad is not trivial. So
some~\gls{dm} techniques are used to gain an understanding of student
performance.

The paper states that the data from the logs is initially transformed to be
inserted into a relational database. SQL is then used to pre-process that data.
Data cube technology is used for multidimensional data viewing. Decision trees
are also constructed from the data.

@@

\TODO{Write this section}

@@

\TODO{Write this section}

@@

Ideas from this paper may be used for later study.

@@

>>>>

Paper is~\cite{ind_007}. Lists a lot of resources for \gls{dm} in \gls{lms}.

@@

What is taken from this paper is the argument that ``(\dots) one of the most
useful~\gls{dm} tasks in e-learning is classification''. The paper then lists a
few sources where~\gls{edm} has been used. They are the following:

\begin{itemize}
    \item Discover potential student groups with similar characteristics and
        reactions to a particular pedagogical strategy;~\cite{ind_008}
    \item Detect students' misuse or game-playing; \TODO{Yet to be explore}
    \item Group students who are hint-driven or failure-driven and find common
        misconceptions that students possess; \TODO{Yet to be explore}
    \item Identify learners with low motivation and find remedial actions to
        lower drop-out rates; \TODO{Yet to be explore}
    \item Predict/classify students when using intelligent tutoring systems;
        \TODO{Yet to be explore}
\end{itemize}

@@

\begin{itemize}
    \item Predicting students' grades from test scores using neural
        networks;~\cite{ind_009}
    \item Predicting student academic success (classes that are successful or
        not) using discriminant function analysis; \TODO{Yet to be explore}
    \item Classifying students using genetic algorithms to predict their final
        grade; \TODO{Yet to be explore}
    \item Predicting a student's academic success (to classify as low, medium
        and high risk classes) using different data mining methods; \TODO{Yet
        to be explore}
    \item Predicting a student’s marks (pass and fail classes) using regression
        techniques in Hellenic Open University data; \TODO{Yet to be explore}
    \item Using neural network models from Moodle logs; \TODO{Yet to be
        explore}
\end{itemize}

@@

@@

\gls{lms} systems, like Moodle, generate logs which describe that activities of
it's users. Those logs contain entries for when students login, when they ask
questions, when they offer proposals on so on. Analysing these logs in order to
understand if student performance is good or bad is not trivial because they
were not made for pedagogical purposes. So some~\gls{dm} techniques are used to
gain an understanding of student performance.

The paper states that the data from the logs is initially transformed to be
inserted into a relational database. SQL is then used to pre-process that data.
Data cube technology is used for multidimensional data viewing. Decision trees
are also constructed from the data. These decision trees constructed from the
web logs are the final results which shed light on student behaviour.

The logs in questions are made in a system that implements IBIS. The logs are
processed and inserted into data cubes for later analysis. The aim of the
analysis is to check if certain pedagogical strategies work. The analysis later
use decision trees.

The paper is too long and repeats a few sections. It is not that clear how the
logs are processed or how SQL and data cubes are used for analysus. It is also
not clear how decision trees are built or what they represent.

This is a useful paper with some different methods worth reading about, even if
data cube isn't that common in the rest of the literature explored until this
point.

@@

This paper is useful because it is an example of mining web logs for~\gls{edm}.
Also useful for it shows the usage of data cubes, which isn't that common.

@@

No further work is done for this paper.

@@

Ideas from this paper may be used for later study, namely how data is divided
into fold for training and testing, how resampling is done to generate more
data, and how it also influences the correctness of the trained models.

@@

% =============================================================================
\section{\texttt{IND\_003} - Web Usage Mining for Predicting Final Marks of
Students That Use Moodle Courses}

Paper is~\cite{ind_003}. Paper~\cite{ind_007} is related to this one, for the
authors and experiments in this paper are the same as in~\cite{ind_007}, but
are presented with much more detail.

This paper mines web logs of~\gls{lms} in order to take meaning from them. Like
in~\cite{ind_007} and~\cite{ind_008}, it is asserted that extracting meaningful
information from logs is not trivial, so~\gls{dm} methodologies are used. The
paper makes it so, while presenting the various algorithms testing with
different dataset, having some of which being the results of resampling.

The paper shows how data from seven courses is taken and mined. That data
consists of web logs detailing the activities of students in Moodle. Those
activities are, for example, when a student logged in, when it answered a
question, when it saw a forum post, etc. Several algorithms are executed over
this data in order to classify students. Further pre-processing tasks are
executed over the same data and differences in accuracy are observed.

We are able to see the results of various algorithms executed with different
datasets. It is possible to observe how different pre-processing methodologies
influence the final results. The paper presents several ways to pre-process
data, and many algorithms.

Looking at all of the results, we see that no algorithm got a better ``Global
Percentage of Correctly Classified'' percentage than 66\%. This level of
accuracy leaves much to be desired. The geometric mean is used to evaluate the
accuracy of algorithms with imbalanced data. We see that many algorithms get
0\% in this indicator, while other got percentages below 50\% and close to 0\%.
This is very bad.

Decision trees are concluded to be the best model for they perform better in
term of ``Global Percentage of Correctly Classified'' and in geometric mean.
These models are best executed with the presented methods for pre-processing.
The final values are still considered to be low, but the results make sense.

Again, we see how using data mining on~\gls{lms} logs is useful. We also see
how classification is useful.

This paper presents a few tools which will be extremely important to
pre-process data in order to prepare it for the algorithms. It is intend that
decision trees are a good model to classify students into different groups
given their activity in Moodle.

Find more about Moodle Data Mining Tool and find more work done by these
authors.

Look further into using decision trees to mine Moodle data.
